---
title       : My Test of Slidify
subtitle    : My subtitle
author      : author
job         : job line
logo        : slidify_logo_big.png
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax, quiz, bootstrap]     # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
--- 


```{r setup, cache = TRUE, echo = F, message = F, warning = F, tidy = F}
# make this an external chunk that can be included in any file
options(width = 100)
opts_chunk$set(message = F, error = F, warning = F, fig.align = 'center', dpi = 100, tidy = T, cache = F, cache.path = '.cache/', fig.path = 'fig/')

options(xtable.type = 'html')
knit_hooks$set(inline = function(x) {
  if(is.numeric(x)) {
    round(x, getOption('digits'))
  } else {
    paste(as.character(x), collapse = ', ')
  }
})
knit_hooks$set(plot = knitr:::hook_plot_html)
```

## Read-And-Delete

1. Edit YAML front matter
2. Write using R Markdown
3. Use an empty line followed by three dashes to separate slides!

--- .class #id 

## Slide 2

Here is some text (Slide 2)

```{r, results='hide'}
set.seed(42)
x <- rnorm(20)
mean(x)
var(x)
```
The first element of **x** is `r round(x[1], 3)`

---

## A Plot

```{r, echo=FALSE, fig.width=9.5, height=6, fig.align='center'}
par(mfcol=c(1,2))
boxplot(x)
hist(x,main='')
par(mfcol=c(1,1))
```

--- .quote

<q>If you think without writing, you only think you're thinking. - Leslie Lamport</q>

--- {class: class1, bg: cyan, id: id1}

## Slide Title

Slide Contents

---

## Mathjax ##

$$
\begin{aligned}
\nabla \times \vec{\mathbf{B}} -\, \frac1c\, \frac{\partial\vec{\mathbf{E}}}{\partial t} & = \frac{4\pi}{c}\vec{\mathbf{j}} \\   \nabla \cdot \vec{\mathbf{E}} & = 4 \pi \rho \\
\nabla \times \vec{\mathbf{E}}\, +\, \frac1c\, \frac{\partial\vec{\mathbf{B}}}{\partial t} & = \vec{\mathbf{0}} \\
\nabla \cdot \vec{\mathbf{B}} & = 0 \end{aligned}
$$

---

<q style="margin-left:140px;">The overriding design goal for Markdown's formatting syntax is to make it as readable as possible. The idea is that a Markdown-formatted document should be publishable as-is, as plain text, without looking like it's been marked up with tags or formatting instructions.</q>

--- &radio

## Question 1

What is 1 + 1?

1. 1
2. _2_
3. 3
4. 4

*** .hint
This is a hint

*** .explanation
This is an explanation




